Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning

### 2014-04-13 FinalPaper/paper.tex
Improve conclusion

Two types of probabilistic planners are MDP solvers and replanners.
Surprisingly replanners performed extremely well in the first IPPC
competitions, especially FF-Replan in IPPC-04. Later, with FH-MDPs replanners
failed to be scalable and sensitive to an expected reward maximization, the
evaluation criteria for those domains. \textsc{Gourmand} is a state-of-the-art
MDP solver that performed better than other planners like \textsc{Glutton} or
PROST.

@@

Finally we described to other relevant planners RFF and PROST\. RFF is a
planner similar to FF-Replan, but instead works off-line and generates
policies. PROST is a UTC based probabilistic planner that outperformed
\textsc{Gourmand}'s predecessor \textsc{Glutton}.

>>>>

Replanners surprisingly performed extremely well in the first IPPC domains,
especially FF-Replan in IPPC-04. The good performance for replanners was
because of the way domains were constructed. Later, with FH-MDPs replanners
failed to be scalable and sensitive to an expected reward maximization, the
evaluation criteria for those domains. \textsc{Gourmand} is a state-of-the-art
MDP solver that performed better than other planners like \textsc{Glutton} or
PROST.

@@

The UAV domain has, like the \textsc{Navigation} domain many probabilities to
hit a dead end, in case a data package is not received correctly. There are
multiple goal trajectories, there can be goal trajectory pairs with the same
initial sequence and if the data package is near the base station the
probability a dead end is reached is decreased. In this case it satisfies the
\emph{probabilistic interestingness} test. \textsc{Gourmand} would be the
preferred planner for the UAV domain. However in real communication systems
failure of communication can often detected using acknowledgements. If a UAV
knows the transmission has failed, it can do something else, so dead ends
disappear from the domain. For such a definition of the UAV domain, a replanner
would work satisfactory. Based on the exact conditions of the domain, a type of
planner can be chosen. If those conditions are slightly tweaked, another type
of planner can be favorable.
